Randomized trace estimation for parameter-dependent matrices applied to spectral density approximation

### 2024-08-20 paper/re-pro-badge.tex
automatically reproduce paper

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/841c60a}{841c60a} on 2024-08-13 at 15:16:51 UTC.

>>>>

The code for our numerical experiments can be found on \url{https://github.com/FMatti/Rand-TRACE}. The figures and tables were generated from the commit \href{https://github.com/FMatti/Rand-TRACE/tree/c1a5f4f}{c1a5f4f} on 2024-08-20 at 15:38:04 UTC.
